Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-19 tex/paper1/paper1.tex
intro to the coronal heating hypothesis

The coronal regions studied here also exhibit \PL-like \PA.  Under the
modeling assumptions of models $M_{1}$ and $M_{2}$, the first
contribution to the observed power spectrum is a \PL.  It is present
in both wavebands studied and in all the regions, and so parsimony
suggests that the mechanism of its creation is both similar and
ubiquitous in all {\bf similar} parts of the solar atmosphere {\bf ,
  that is quiet Sun, moss, loop footpoints and above sunspots}.
Further, \cite{2014AA...563A...8A} show that a \PL\ \PS\ is present in
time-series of coronal active region and quiet Sun emission over the
frequency range 0.01 - 1 mHz, overlapping with the frequency studied
in this paper.  We hypothesize that the \PL\ \PS\ in the coronal
171\AA\ and 193\AA\ emission is due to the sum of a distribution of a
large number of events having different amounts of emission.
\cite{2011soca.book.....A} describes how a \PL\ \PS\ may obtained from
such a distribution, and that argument is outlined below.

>>>>

{\bf The coronal regions studied here also exhibit \PL-like \PA\ in the
approximate frequency range $0.05\rightarrow 10$ mHz.  Under the
modeling assumptions of models $M_{1}$ and $M_{2}$, the first
contribution to the observed power spectrum is a \PL\ (which is
detectable in all regions up to about 2 mHz)}.  It is present in both
wavebands studied and in all the regions, and so parsimony suggests
that the mechanism of its creation is both similar and ubiquitous in
all {\bf similar} parts of the solar atmosphere {\bf , that is quiet
  Sun, moss, loop footpoints and above sunspots}.  Further,
\cite{2014AA...563A...8A} show that a \PL\ \PS\ is present in
time-series of coronal active region and quiet Sun emission over the
frequency range 0.01 - 1 mHz, overlapping with the frequency studied
in this paper.  We hypothesize that the \PL\ \PS\ in the coronal
171\AA\ and 193\AA\ emission is due to the sum of a distribution of a
large number of events having different amounts of emission.
\cite{2011soca.book.....A} describes how a \PL\ \PS\ may obtained from
such a distribution, and that argument is outlined below.
